### 2018-10-31 Sections/economics_of_the_quantum_internet.tex
Geo localisation

>>>>

%
% Geographic Localisation
%

\subsection{Geographic localisation}\index{Geographic localisation}\label{sec:geo_loc}

Because of the resource overheads associated with performing computations in a distributed manner, e.g via the resource costs associated with long-range repeater networks\index{Quantum repeater networks}, there is an economic imperative to localise quantum infrastructure, so as to mitigate this -- there is a clear economic benefit associated with housing qubits in close geographic proximity such that no long-distance quantum channels are required.

However, it's undesirable to \textit{entirely} centralise infrastructure of any type, for two primary reasons:
\begin{itemize}
	\item Geo-strategic competition\index{Geo-strategic politics}: competing nation states may not want essential infrastructure to be located entirely offshore, placing them at the mercy of their strategic competitors.
	\item Geographical redundancy\index{Geographical redundancy}: to eliminate single points of failure\index{Single points of failure} (SPOF), which undermine network robustness, it is desirable for infrastructure to be geographically segregated. In present-day large-scale distributed classical platforms, geographical redundancy is a key consideration. Even though it would be most efficient if all data were completely centralised, obviating communications overheads, it would be catastrophic if a single earthquake could decimate the entire system.
\end{itemize}

Thus, we can reasonably anticipate that the quantum internet will not evolve like the classical `internet of things', whereby super-small computational resources are scattered across the globe. Rather, a relatively small number of central `hubs' are likely to emerge, which centralise enormous computational power, but which interconnect via the quantum internet to form the globally unified quantum cloud (Sec.~\ref{sec:glob_unif_quant_cloud}).

Much like the classical internet, it's to be expected the network that will emerge that will emerge will approximate a scale-free network (Sec.~\ref{sec:scale_free_networks})\index{Scale-free networks}, with a very hierarchical structure, following a Pareto distribution\index{Pareto distribution} in hub-size.
